Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-26 src/tex/conclusion.tex
methods.tex is mostly finished but w/o citations
disc section

@@

\bruce{have subsection in results.tex to discuss the astro interpretation of our results and connect to literature. 
I think main points for conclusion are to sum up conclusions with one last call to literature for most important parts, 
followed by short discussion of the outlook going into O4 and how this method will be especially useful as we rapidly approach
GW's data rich era}

>>>>

\section{Discussion}\label{sec:astrodiscussion}

\bruce{Here we discuss the astrophysical implications of work -- connect to wider literature}

@@

\bruce{main points for conclusion are to sum up conclusions with one last call to literature for most important parts, 
followed by short discussion of the outlook going into O4 and how this method will be especially useful as we rapidly approach
GW's data rich era}

### 2022-09-26 src/tex/intro.tex
disc section

Polynomial splines have been applied to success across different areas of gravitational-wave astronomy. They have been used to model the gravitational-wave data noise spectrum, 
detector calibration uncertainties, coherent gravitational waveform deviations, and modulations to a power law mass distribution \cite{Littenberg_2015,Edwards_2018,B_Farr_etal_2014,Edelman_2021,Edelman_2022ApJ}
In this paper we highlight how the use of basis-splines can provide a powerful non-parametric modeling approach to the astrophysical distributions of compact 
binaries. We illustrate how one can efficiently model the mass and spin distributions of compact binaries in GWTC-3 with basis splines to infer population properties using 
hierarchical Bayesian inference. We discuss our results in the context of current literature on compact object populations and how this method complements the simpler lower dimensional parametric models. 
This data-drien approach will be capable of finding more subtle features, that may not be expected, should they appear in future catalogs. 
In Section \ref{sec:basis_splines} we go over the background of basis splines, in Section \ref{sec:results} we present results using our basis 
spline model on the mass and spin distributions of BBHs in GWTC-3, followed by discussing results in their astrophysical context and concluding in Section \ref{sec:conclusion}.

>>>>

Polynomial splines have been applied to success across different areas of gravitational-wave astronomy. They have been used to model the gravitational-wave data noise spectrum, 
detector calibration uncertainties, coherent gravitational waveform deviations, and modulations to a power law mass distribution \cite{Littenberg_2015,Edwards_2018,B_Farr_etal_2014,Edelman_2021,Edelman_2022ApJ}
In this paper we highlight how the use of basis-splines can provide a powerful non-parametric modeling approach to the astrophysical distributions of compact 
binaries. We illustrate how one can efficiently model the mass and spin distributions of compact binaries in GWTC-3 with basis splines to infer population properties using 
hierarchical Bayesian inference. We discuss our results in the context of current literature on compact object populations and how this method complements the simpler lower dimensional parametric models. 
This data-drien approach will be capable of finding more subtle features, that may not be expected, should they appear in future catalogs. 
In Section \ref{sec:basis_splines} we go over the background of basis splines, in Section \ref{sec:results} we present results using our basis 
spline model on the mass and spin distributions of BBHs in GWTC-3, followed by discussing results in their astrophysical context Section \ref{sec:astrodiscussion} 
and concluding in Section \ref{sec:conclusion}.
